Capstone Movielens Report

### 2025-12-07 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report section updated: UMGYE Model Regularization: Pre-configuration.

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization] of [Appendix A: Support Functions], respectively.
:::

>>>>

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) are described in the sections *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UME Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

### 2025-12-07 reports/capstone-movielens.site/02.6.UMGE-model.Rmd
Report section updated: UMGYE Model Regularization: Pre-configuration.

As we explain earlier in the [UME Model Regularization: *Pre-configuration*], we need to do some pre-configuration to determine a suitable range of $\lambda$ for subsequent fine-tuning of our current model.

@@

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGE Model: Regularization] of [Appendix A: Support Functions], respectively.
:::

>>>>

As we explained earlier in the [UME Model Regularization: *Pre-configuration*], we need to do some pre-configuration to determine a suitable range of $\lambda$ for subsequent fine-tuning of our current model.

@@

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report section updated: UMGYE Model Regularization: Pre-configuration.

Let's perform the pre-configuration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:

We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions], passing the [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.

@@

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1493) script on _GitHub_.
:::

@@

>>>>

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be found in the [UMGYE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1224) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1224) script on _GitHub_.
:::

As for previous models, we will use the function [tune.model_param](#func.tune.model_param) passing in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument the model-specific helper function (this time designed for the *UMGYE Model*): [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv).

::: {.noteblock data-latex=""}
The functions [tune.model_param](#func.tune.model_param) and [regularize.test_lambda.UMGY_effect.cv](#func.regularize.test_lambda.UMGY_effect.cv) are described in the sections *Common Helper Functions /* [ Regularization Functions](#appndx_a.CHF.regularization) and  *Models Training: Support Functions /* [UMGYE Model: Regularization], respectively, of [Appendix A: Support Functions].
:::

@@

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the custom data visualization function [data.plot](#func.data.plot) described in the *Data Helper Functions /* [Data Visualization Functions] section of [Appendix A: Support Functions].
:::
